---
title: "New project"
author: "Lucas Gauer"
date: "Last update : `r format(Sys.time(), '%d %B %Y')`"
output: 
  rmdformats::downcute:
    toc_depth: 3
    number_sections: false
    use_bookdown: true
    downcute_theme: "chaos"
    self_contained: yes
    lightbox: true
    gallery: true
    highlight: tango
bibliography: references.bib
csl: vancouver.csl
link-citations: yes
---

```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

# Project management

### File structure :

In `data/` : original raw data (untouched).

-   `sub-XXX/` : a data folder for every patient

    -   `agenda_mig.xlsx` : example of migraine agenda of patient "sub-XXX"
    -   `agenda_mig_vars.xlsx` : description of used variables (same for all patients)

-   `subject_db.xlsx` : list of all patients and some demographic features

-   `subject_db_var_description.xlsx` : description of variables used in `patient.xlsx` table.

In `markdown/` :

-   `raw_scripts/extracted/` : R scripts automatically extracted from Markdown documents in `markdown/sections`.
-   `sections/` : Markdown scripts used to process data.
-   `inserts/` : objects to import (*ie.* images generated elsewhere).
-   `main_doc.Rmd` : Main working/synthetic document and HTML version to share and review.
-   `references.bib` : bibliography file used in this document.
-   `vancouver.csl`: citation format used in this document (Vancouver numeric).

In `output/` (this folder is automatically created when running code in this document) :

-   `sub-xxx/` : contains intermediate files automatically saved during processing.
-   `figs/` : figures generated during the processing.
-   `complete_extracted_table.csv` : summary across all patients (Excel-friendly CSV).
-   `complete_extracted_table.RData` : summary across all patients (RData file).

### Memo : How to link to Github from existing folder

1.  Open `template-proj.Rproj`, then run `usethis::use_git()`.
2.  Create an empty `project-name` GitHub repo.
3.  Open a terminal and `cd` to `template-proj.Rproj` place.
4.  Run `git push` commands :

```{bash eval=FALSE}
git remote add origin git@github.com:Username/project-name.git
git push -u origin master
```

### Libraries used in this project

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl) # Installed with tidyverse but loads separately
library(hablar) # To easily assign types of variables after data importation.
library(lubridate) # Installed with tidyverse but loads separately
library(zoo) # use for rolling average easy computation with rollapplyr
library(gtsummary) # Easy summary tables
library(hrbrthemes) # Nice themes for ggplot

# HTML files are knitted using "bookdown" and
# with the downcute template from "rmdformats".
```

### Retrieve and extract individual scripts

```{r message=FALSE, results='hide'}
# Define where are the Rmarkdown files and found them all :
sections.path <- file.path(rprojroot::find_root("template-proj.Rproj"),
                           "markdown",
                           "sections")
r.files.vec <- list.files(sections.path)
r.files.vec <- r.files.vec[grepl(".Rmd", r.files.vec)]

# Define where the extracted R files will be stored :
extracted.path <- file.path(rprojroot::find_root("template-proj.Rproj"),
                            "markdown",
                            "raw_scripts",
                            "extracted")

# Extract the R code from all found Rmarkdown files :
extract.my.rmds = function(file.i) {
  file.name <- gsub(".Rmd", "", file.i)
  extracted.file <- paste0(file.name, ".R")
  knitr::purl(file.path(sections.path, file.i),
              file.path(extracted.path, extracted.file))
  }
# Extract them : 
map(r.files.vec, extract.my.rmds)
```

### List of available scripts

List of all available scripts in the project :

```{r echo=FALSE}
writeLines(list.files(extracted.path))
```

Ordered list of currently used scripts :

```{r}
# Add here the list of extracted R files we want to run sequentially :
source.vec <- c(
  "import_raw_data.R",
  "table_example.R",
  "graph_example.R"
  )
```

```{r eval=FALSE, include=FALSE}
#### Dev use : Run all scripts in the order decided of source.vec.
# This chunks loads all objects from called scripts in the current environment, allowing for easy work on updated data. 
# Set eval to TRUE to use this chunk.

source.my.rmds = function(source.i) {
  source(file.path(extracted.path, source.i))
  }
# Run them :
map(source.vec, source.my.rmds)
```

# Data processing

## Introduction

Add some background, methodology or references to critically important papers. [@mudge2004] The `references.bib` file is updated using Rstudio citation tool. Vancouver format is used here, but you can replace the `vancouver.csl` file by any other format (find some examples [here](https://www.zotero.org/styles) ).

Also add some images that have nothing to do with figures generated from this project. The HTML is self-contained, so it's heavier but you can share it without worrying about broken links in embedded graphics.

![[<https://xkcd.com/1945/>](https://xkcd.com/1945/)](inserts/image_example.png "example image")

## Data import

First, import and pre-process data with `import_raw_data.R`

```{r file=paste0(extracted.path,"/",source.vec[1]), eval=TRUE, results='hide', collapse=TRUE}
```

## Results

### Simple table

We show here a simple example summary table with `table_example.R`.

```{r file=paste0(extracted.path,"/",source.vec[2]), eval=TRUE, results='asis', collapse=TRUE}
```

### Simple plot

We show here a simple example of plot with `graph_example.R`.

```{r file=paste0(extracted.path,"/",source.vec[3]), eval=TRUE, results='asis', collapse=TRUE}
```

# References
